Our Future Nuclear Data Needs

### 2018-12-17 nuclear_data_needs/nuclear_data_needs.tex
Added new 239pu_nn figure

%Authors, affiliations address.
\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^6$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^7$
\affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
\affil{$^2$Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
\affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
\affil{$^6$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
\affil{$^7$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}

@@

@@

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.8\linewidth]{rotated_swings.pdf}

@@

One significant source of (n,xn$\gamma$) partial cross section data from 1997 to 2003 was the GEANIE collaboration (Germanium Array for Neutron-Induced Excitations) at the Los Alamos Neutron Science Center/Weapons Neutron Research (LANSCE/WNR) facility.
While the primary goal of the GEANIE collaboration was the determination of the \ce{^{239}Pu}(n,2n) cross section \cite{Ber02}, it resulted in the publication of more than two dozen papers over the course of more than 15 years.
 Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
 It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.

@@

Over the past several years, work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including \ce{^{238}U}, \ce{^{239,240,242}Pu} and \ce{^{232}Th} \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.

Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter ($\sigma$) of the form: 
\begin{equation}\label{eqn:spin_cutoff}
\sigma\pp{E_x}=0.01389 \dfrac{A^{5/3}}{\widetilde{a}}\sqrt{aU}
\end{equation}
where $U$ is roughly the $E_x$ minus the pairing gap $\Delta$, $a$ is the level density parameter, $A$ is the nuclear mass and $\widetilde{a}$ is the asymptotic level density value one would obtain in the absence of any shell effects.

@@

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.7\linewidth]{fig3.pdf}

>>>>

%Authors, affiliations address.
\author{Lee A. Bernstein$^{1,2}$, David A. Brown$^3$, \\Arjan J. Koning$^4$, Brad T. Rearden$^5$,  \\Catherine E. Romano$^5$, Alejandro A. Sonzogni$^3$, Andrew S. Voyles$^{1,2}$, and Walid  Younes$^6$
\affil{$^1$Nuclear Science Division, Lawrence Berkeley National Laboratory,  Berkeley, CA 94720, USA; email: labernstein@lbl.gov}
\affil{$^2$Department of Nuclear Engineering, University of California, Berkeley,  Berkeley, CA 94720, USA}
\affil{$^3$National Nuclear Data Center, Brookhaven National Laboratory, Upton, NY 11973, USA}
\affil{$^4$Arjan's affiliations\textred{Arjan - please provide!}}
% \affil{$^5$Brad's affiliations\textred{Brad - please provide!}, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
\affil{$^5$Reactor and Nuclear Systems Division, Oak Ridge National Laboratory, Oak Ridge, TN 37830, USA}
\affil{$^6$\textred{Add Walid's division here}, Lawrence Livermore National Laboratory,  Livermore, CA 94550, USA}}

@@

\begin{figure}[b]
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.7\linewidth]{rotated_swings.pdf}

@@

@@

One significant source of (n,xn$\gamma$) partial cross section data from 1997 to 2003 was the GEANIE collaboration (Germanium Array for Neutron-Induced Excitations) at the Los Alamos Neutron Science Center/Weapons Neutron Research (LANSCE/WNR) facility.
While the primary goal of the GEANIE collaboration was the determination of the \ce{^{239}Pu}(n,2n) cross section \cite{Ber02}, it resulted in the publication of more than two dozen papers over the course of more than 15 years.
 Experiments were run on all three of the major Actinides: \ce{^{235}U} \cite{You01}, \ce{^{239}Pu} \cite{Ber02} and \ce{^{238}U} \cite{Fot04}.
 GEANIE produced the first high-resolution partial $\gamma$-ray cross section data on the \enquote{Big 3}.
This includes one of the first results for \ce{^{239}Pu}(n,n'$\gamma$), shown in \autoref{fig:239pu_nn_cropped}  together with calculations using the CoH reaction modeling code developed by Toshihiko Kawano. 
% It should be noted that the GEANIE data was angle-integrated with respect to the outgoing neutron, limiting its value for neutron transport modeling.
 It should be noted that GEANIE did not include any neutron detectors, producing only angle-integrated partial $\gamma$-ray cross sections.

\begin{figure}[t]
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.6\linewidth]{239pu_nn_cropped.pdf}

 % variation_curve.pdf: 612x792 pixel, 72dpi, 21.59x27.94 cm, bb=0 0 612 792
 \caption{A selection of the \ce{^{239}Pu}(n,n'$\gamma$) partial $\gamma$-ray cross sections from \cite{Ber00} for the two transitions de-exciting the ${^5/_2}^{+}$ level at $E_x=$285.46 keV.}
 \label{fig:239pu_nn_cropped}
\end{figure}

@@

Over the past several years, work led by the group at the University of Oslo has shown that there is a surprisingly large amount of M1 radiative strength believed to be a type of \enquote{scissors} collective mode throughout the Actinide mass region near the valley of stability including \ce{^{238}U}, \ce{^{239,240,242}Pu} and \ce{^{232}Th} \cite{Lap16, Gut13, Gut13a, Gut14, Gut15}.
Other results from the Oslo group show that Actinide NLDs appears to follow a constant temperature (CT) form with a roughly Gaussian dependence on angular momentum that is often described via an energy-dependent width spin cut-off parameter ($\sigma$) of the form: 
\begin{equation}\label{eqn:spin_cutoff}
\sigma\pp{E_x}=0.01389 \dfrac{A^{5/3}}{\widetilde{a}}\sqrt{aU}
\end{equation}
where $U$ is roughly the $E_x$ minus the pairing gap $\Delta$, $a$ is the level density parameter, $A$ is the nuclear mass and $\widetilde{a}$ is the asymptotic level density value one would obtain in the absence of any shell effects.

\begin{figure}
 \centering
%  \includegraphics[clip=true,trim=1.5in 3.4in 1.8in 3.5in, scale=0.8]{./figures/variation_curve.pdf}
 \includegraphics[width=0.55\linewidth]{fig3.pdf}

@@
